Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex

\item We exploit a CEGIS-based approach that uses inductive synthesis
together with a bit-precise formal verification algorithm for synthesising
correct-by-design robust digital controllers for non-fragile closed-loop
stability.

\item Experimental results with our synthesiser show that the
combination of interval arithmetic to represent the controller coefficients
and a two-stage verification approach to continuously refine precision
enables us to compute a parametric, sound solution for $14$ out of $15$
digital stabilizing controllers for a set of continuous and discrete plants
with parametric uncertainties.

@@

%------------------------------------
\subsection{Stability under FWL and Noise}
\label{sec:stability}
%------------------------------------

Correct synthesis of the digital controller requires consideration of the
effect of FWL in controller and quantisation noises in the closed loop
system.  Let the quantiser $Q1$ be the source of a white noise $\nu_{1}$ and
$Q2$ be the source of a white noise $\nu_{2}$.  The following equation
models the system in Figure~\ref{fig:sampledsystem}, encompassing the
parametric uncertainties $\Delta \vec{G}$ and the FWL effects on
the controller ($\hat{C}(z)$):
%
\begin{equation}
\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
\end{equation}
%
The above can be rewritten as follows:
%
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
\end{equation}
%
where
%
\begin{equation}
H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}
%
and
%
\begin{equation}
H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)}.
\end{equation}

\begin{myassumption}
\label{whitenoise}
%
The quantisation noises $\nu_{1}$ (from $Q1$) and $\nu_{2}$ (from $Q2$) are
uncorrelated white noises and their amplitudes are always bounded by the
half of quantisation step~\cite{astrom1997computer}, i.e., $\vert \nu_{1}
\vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$,
where $q_{1}$ and $q_{2}$, respectively, are the quantisation steps of ADC
and DAC.
% 
\end{myassumption}

@@

Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for the
ability of a digital controller to stabilize the closed loop system,
considering plant parametric uncertainties (i.e., $\Delta_p \vec{G}$),
quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control
software.  Based on it, the model for plant uncertainty due quantisation
noise (i.e., $\Delta_q \vec{G}$) may be disregarded if the conditions on
Lemma~\ref{lemma:eq_int_stab} are satisfied and if the quantisation noise is
bounded.  The boundedness of the quantisation noise is
assumption~\ref{whitenoise}.

>>>>

\item We designed and implemented an automatic approach for 
generating {\em corect-by-construction} digital controllers that is 
based on state-of-the-art inductive synthesis techniques.
Our application of program synthesis is non-trivial 
and requires addressing challenges specific to
control systems such as the effects of quantisers 
and FWL. In particular, we found that a two-stage 
verification engine that continuously refines the precision
of the fixed-point representation is key to the performance of our approach
(the increase in speed over a conventional one-stage verification 
approach is in most cases of several orders of magnitude).

\item We provide experimental results showing that
our fully automatic program synthesis based approach is able to synthesise 
stable controllers
%sound parametric solutions for digital stabilizing controllers
for a set of intricate benchmarks taken from 
the literature in a reasonable amount of time 
(the median runtime for our benchmark set is 197s, 
implying that half of the controllers can be synthesised in less
than 5 minutes).

%% \item We exploit a CEGIS-based approach that uses inductive synthesis
%% together with a bit-precise formal verification algorithm for synthesising
%% correct-by-design robust digital controllers for non-fragile closed-loop
%% stability.

%% \item Experimental results with our synthesiser show that the
%% combination of interval arithmetic to represent the controller coefficients
%% and a two-stage verification approach to continuously refine precision
%% enables us to compute a parametric, sound solution for $14$ out of $15$
%% digital stabilizing controllers for a set of continuous and discrete plants
%% with parametric uncertainties.

@@

%------------------------------------
\subsection{On the stability considering effects of implementation issues and quantisation noises}
\label{sec:stability}
%------------------------------------

In order to obtain a sound synthesis of the digital controller, the effect
of FWL implementation in controller and quantisation noises in closed loop
system have to be considered.  Considering that the quantiser $Q1$ is the
source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise
$\nu_{2}$, the following equation is written for the system in
Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties
$\Delta \vec{G}$ and the FWL effects on controller ($\hat{C}(z)$):
%
\begin{equation}
\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
\end{equation}
%
that can be rewritten as follows:
%
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
\end{equation}
%
where
%
\begin{equation}
H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}
%
and
%
\begin{equation}
H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}

\begin{myassumption}
\label{whitenoise}
%
The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are uncorrelated white noises and their amplitudes are always bounded by the half of quantisation step \cite{astrom1997computer}, {\it i.e.} $\vert \nu_{1} \vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$, where $q_{1}$ and $q_{2}$ are respectively the quantisation step of  ADC and DAC.
% 
\end{myassumption}

@@

The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for
synthesis of digital controllers able to stabilize closed loop system,
considering plant parametric uncertainties ({\it i.e.}, $\Delta_p \vec{G}$),
quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital
controllers.  Based on it, the model for plant uncertainty due quantisation
noise ({\it i.e.}, $\Delta_q \vec{G}$) may be disregarded if the conditions
on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise
is bounded.  The quantisation noise is indeed bounded, since the following
assumption~\ref{whitenoise}.
